Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2023-02-10 manuscript/manuscript.tex
test overleaf commit. only a test comment, feel free to undo this

Densities of typical water models can be found in the \software{cpptraj} manual.
We also provide the densities for water models commonly used with AMBER forcefields in table \ref{tab:ref_densities}.
These densities were calculated from \SI{1}{\micro\second}\pdfcomment{weird small mu symbol} MD simulations at \SI{1}{\bar} and \SI{300}{\kelvin} using the Berendsen barostat and the Langevin thermostat.
The water boxes were prepared with \software{tleap} to a size of \SI{100 x 100 x 100}{\angstrom} before pressure equilibration.
\todo{vah -> Finish these calculations}
\begin{table}[h]
	\caption{Reference density $\rho_0$ and mean water-water energy $E_{ww, norm}$ for various water models from NpT simulations at 300K/1bar.}\label{tab:ref_densities}
	\small
	\begin{tabularx}{\columnwidth}{@{}lrr@{}}
		\toprule
		Water Model       & $\rho_0$ /\AA$^{-3}$ & $E_{ww, norm}$ /$kcal\cdot mol^{-1} \cdot water^{-1}$  \\
		\midrule
		TIP3P    & 0.0329 & -9.533   \\
		TIP3PFB  & 0.0334 & -11.369  \\
		TIP4P    & 0.0332 & -9.856   \\
		TIP4P/Ew & 0.0332 & -11.036  \\
		TIP5P    & 0.0329 & -9.596   \\
		SPC/E    & 0.0333 & -11.123  \\
		OPC      & XXXX   & XXXX     \\
		OPC3     & XXXX   & XXXX     \\
		POL3     & XXXX   & XXXX     \\
		\bottomrule
	\end{tabularx}
\end{table}
If your simulation settings diverge significantly from the above setting or for other solvent models not listed either here or in the \software{cpptraj} manual, the density should be computed from a pure solvent simulation beforehand.

@@

Using the \inlinecode{energy} command in \software{cpptraj}, you can compute this interaction energy.
We recommend using PME in combination with PME-GIST, but not with GPU-GIST\@.
An example \software{cpptraj} input might look like:
\begin{lstlisting}[style=cpptraj]
parm solvated.parm7
trajin md-01.nc 1 last 100
energy complex ^1,2 # etype pme
energy strept ^1 # etype pme
energy biotin ^2 # etype pme
go
diff = complex[total] - strept[total] - biotin[total]
writedata energy.dat diff complex[total] \
strept[total] biotin[total]
avg(complex[total])
avg(strept[total])
avg(biotin[total])
avg(diff)
\end{lstlisting}

@@

>>>>

Densities of typical water models can be found in the \software{cpptraj} manual.
We also provide the densities for water models commonly used with AMBER forcefields in table \ref{tab:ref_densities}.
These densities were calculated from \SI{1}{\micro\second}\pdfcomment{weird small mu symbol} MD simulations at \SI{1}{\bar} and \SI{300}{\kelvin} using the Berendsen barostat and the Langevin thermostat.
The water boxes were prepared with \software{tleap} to a size of \SI{100}{\angstrom} x \SI{100}{\angstrom} x \SI{100}{\angstrom} before pressure equilibration.
\todo{vah -> Finish these calculations}
\begin{table}[h]
	\caption{Reference density $\rho_0$ and mean water-water energy $E_{ww, norm}$ for various water models from NpT simulations at 300K/1bar.}\label{tab:ref_densities}
	\small
	\begin{tabularx}{\columnwidth}{@{}lrr@{}}
		\toprule
		Water Model       & $\rho_0$ /\AA$^{-3}$ & $E_{ww, norm}$ /$kcal\cdot mol^{-1} \cdot water^{-1}$  \\
		\midrule
		TIP3P    & 0.0329 & -9.533   \\
		TIP3PFB  & 0.0334 & -11.369  \\
		TIP4P    & 0.0332 & -9.856   \\
		TIP4P/Ew & 0.0332 & -11.036  \\
		TIP5P    & 0.0329 & -9.596   \\
		SPC/E    & 0.0333 & -11.123  \\
		OPC      & XXXX   & XXXX     \\
		OPC3     & XXXX   & XXXX     \\
		POL3     & XXXX   & XXXX     \\
		\bottomrule
	\end{tabularx}
\end{table}
If your simulation settings diverge significantly from the above setting or for other solvent models not listed either here or in the \software{cpptraj} manual, the density should be computed from a pure solvent simulation beforehand.

@@

Using the \inlinecode{energy} command in \software{cpptraj}, you can compute this interaction energy.
We recommend using PME in combination with PME-GIST, but not with GPU-GIST\@.
An example \software{cpptraj} input might look like:
\begin{lstlisting}[style=cpptraj]
parm solvated.parm7
trajin md-01.nc 1 last 100
energy complex ^1,2 # etype pme
energy strept ^1 # etype pme
energy biotin ^2 # etype pme
go
diff = complex[total] - strept[total] - biotin[total]
writedata energy.dat diff complex[total] \
strept[total] biotin[total]
avg(complex[total])
avg(strept[total])
avg(biotin[total])
avg(diff)
\end{lstlisting}
% test edit

@@

A more sophisticated visualization, including the energy, entropy, and free energy of removing a single water molecule, is found in Figure~\ref{fig-binding-pocket.png}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{figures/binding-pocket-energy-levels.png}
	\caption{Biotin in the streptavidin binding pocket, with isosurfaces based on the GIST calculation on the holo structure. Green: negative entropy ($T\Delta S$). Blue: negative energy (based on $E_{sw} + 2E_{ww}$). Red: positive energy. Isolevels are ($\pm$) 0.25, 0.5, 1.0, 1.5, 2.0, 2.5, and 3.0, except for the positive energy, where they are divided by two.}\label{fig-binding-pocket.png}
\end{figure}
